%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\usepackage{calc} % added
\newcommand{\resumeSubSubheadingLeft}[2]{% % added
\begin{description}[leftmargin=!,labelwidth=\widthof{\small\bfseries #1}]
    \item[\small #1]{\textit{\small  #2}}
\end{description}
}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Varun Ramani} \\ \vspace{1pt}
    \small \href{tel:7326725930}{\underline{732-672-5930}} $|$ \href{mailto:varun.ramani@gmail.com}{\underline{varun.ramani@gmail.com}} $|$ 
    \href{https://linkedin.com/in/varun-ramani}{\underline{linkedin.com/in/varun-ramani}} $|$
    \href{https://github.com/varun-ramani}{\underline{github.com/varun-ramani}} $|$
    \href{https://varunramani.com}{\underline{varunramani.com}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Maryland}{College Park, MD}
      {B.S. Computer Science, Minor in Mathematics. GPA 3.9/4.0.}{Aug. 2020 -- May 2024}
      \resumeSubSubheadingLeft
        {Relevant Coursework}{Data Structures/Algorithms, Machine Learning, Networks, Cryptography \\ Multivariate Calculus, Linear Algebra, Statistics, Abstract Algebra, Compilers}
  \resumeSubHeadingListEnd

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Java, JavaScript, C/C++, Go, OCaml, Ruby, SQL, MATLAB} \\
     \textbf{Frameworks}{: Flask, React, React Native, Flutter, Keras} \\
     \textbf{Tooling and Systems}{: Git, AWS, Google Cloud Platform, Heroku, Docker, Linux} \\
     \textbf{Libraries}{: pandas, NumPy, Matplotlib}
    }}
 \end{itemize}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
    {Student Trainee}{Jun. 2023 -- Aug. 2023}
    {Naval Research Laboratory}{Washington, D.C.}
      \resumeItemListStart
        \resumeItem{Designing and developing modernized tooling for RADAR applications.}
        \resumeItem{Collaborate directly with internal clientele to translate requirements into intuitive and performant technology.}
      \resumeItemListEnd
    \resumeSubheading
      {Software Engineering Intern}{May 2022 -- Aug. 2022}
      {Meta Platforms}{Menlo Park, CA}
      \resumeItemListStart
        \resumeItem{Completed and deployed improved identity matching system to Facebook's products.}
        \resumeItem{Created new experiment framework to assess effects of new system in identity matching backend.}
        \resumeItem{Applied Hack, Python, and Meta's internal tooling.}
      \resumeItemListEnd

    \resumeSubheading
      {Teaching Assistant (Data Science / Intro to Computer Systems)}{Aug. 2022 -- Jun. 2023}
      {University of Maryland}{College Park, MD}
      \resumeItemListStart
        \resumeItem{Mentored groups of up to 40 students in systems/UNIX-related concepts.}
        \resumeItem{Clarified concepts pertaining to statistics and machine learning.}
        \resumeItem{Graded projects and exams.}
      \resumeItemListEnd

    \resumeSubheading
      {Undergraduate Research Assistant}{Aug. 2020 -- Dec. 2021}
      {The First-Year Innovation \& Research Experience @ University of Maryland}{College Park, MD}
      \resumeItemListStart
        \resumeItem{Collaboratively implemented machine learning model backed by UNet architecture to perform semantic segmentation on LIDAR data.}
        \resumeItem{Presented at undergraduate research summit.}
      \resumeItemListEnd

% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Memaid} $|$ \emph{Computer Vision, Speech To Text, NLP}}{Apr. 2022}
          \resumeItemListStart
            \resumeItem{Dementia aid. When someone introduces themselves to user, app memorizes face after \textit{only seeing it once} and associates with name. Listens to subsequent conversation and stores highlights.}
            \resumeItem{On future interactions with this person, app automatically recognizes face and relays name / previous highlights to user through connected earbuds.}
            \resumeItem{Won best hack for social good + best use of Google Cloud against 91 competing teams.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Maskif.ai} $|$ \emph{Computer Vision, IoT, Flask Framework}}{Nov. 2020}
          \resumeItemListStart
            \resumeItem{Enforces pandemic mask compliance. Applies computer vision to intelligently trigger WiFi-enabled lock when unmasked individual approaches business's door; automatically unlocks after individual leaves.}
            \resumeItem{Highly cost effective. Leverages Google Assistant SDK to support wide variety of smart locks; fault-tolerant algorithm accurate even with lower-quality cameras.}
            \resumeItem{Beat 42 competing teams for first place at Yale's YHack 2020 hackathon.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Intellicity} $|$ \emph{Computer Vision, MongoDB, Flutter, Flask}}{Sep. 2019}
          \resumeItemListStart
            \resumeItem{Advanced mobile map application. Applies crowdsourced information and vision to add rich, granular details to Google Maps; includes precise geolocation data for trash bins, bathrooms, safety hazards, and parking spots.}
            \resumeItem{Helps people navigate unfamiliar places with confidence; instantly finding what they need.}
            \resumeItem{Ranked top 30 among 242 competing teams.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd








%-------------------------------------------
\end{document}
