%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
\usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\usepackage{calc} % added
\newcommand{\resumeSubSubheadingLeft}[2]{% % added
\begin{description}[leftmargin=!,labelwidth=\widthof{\small\bfseries #1}]
    \item[\small #1]{\textit{\small  #2}}
\end{description}
}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Varun Ramani} \\ \vspace{1pt}
    \small \href{tel:7326725930}{\underline{732-672-5930}} $|$ \href{mailto:varun.ramani@gmail.com}{\underline{varun.ramani@gmail.com}} $|$ 
    \href{https://linkedin.com/in/varun-ramani}{\underline{linkedin.com/in/varun-ramani}} $|$
    \href{https://github.com/varun-ramani}{\underline{github.com/varun-ramani}} $|$
    \href{https://varunramani.com}{\underline{varunramani.com}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Maryland}{College Park, MD}
      {B.S./M.S. Computer Science, Minor in Mathematics. GPA 3.9/4.0.}{Aug. 2020 -- Dec 2024}
        \textit{\small{\item{
          \textbf{Computer Science Coursework}{: Operating Systems, Networks, Compilers, Machine Learning, Data Science, Algorithms/Data Structures} \\
          \textbf{Math Coursework: }{Signal Processing, Cryptography, Abstract Algebra, Linear Algebra, Statistics, Calculus}
        }}}
  \resumeSubHeadingListEnd

%



%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
    {Naval Research Laboratory}{Jun. 2023 -- Aug. 2023}
    {Software Engineering Intern}{Washington, D.C.}
      \resumeItemListStart

        \resumeItem{Revolutionized critical C\# RADAR app and accelerated load
        times by 98\% by rebuilding in \textbf{TypeScript}, \textbf{React}, and
        \textbf{Mantine}.} 

        \resumeItem{Provided military-grade security for app by implementing
        \textbf{mTLS}-based authentication against DoD common access card.} 

        \resumeItem{Decreased prod. build times by 25\% and dev. build times by
        99.96\% by creating \textbf{Docker/Python}-based build system.} 

        \resumeItem{Reduced network traffic by 20\% by analyzing old \textbf{TCP}-based
        app/server communication protocol and optimizing+rebuilt in JSON/HTTP.} 

        \resumeItem{Furthered productivity during legacy backend development by
        using \textbf{Rust} to create efficient compatibility layer for new protocol.}

        \resumeItem{Increased automation by 92\% in software installation
        process by developing modern deployment system using \textbf{Tauri
        (Rust/React)}.}

      \resumeItemListEnd
    \resumeSubheading
      {Meta}{May 2022 -- Aug. 2022}
      {Software Engineering Intern}{Menlo Park, CA}
      \resumeItemListStart

        \resumeItem{Enhanced Facebook user privacy by using industry-standard
        hashing techniques to securely anonymize data and simulating impact.}

        \resumeItem{Optimized core module to realize lower CPU use and
        \textbf{billions of saved operations} by proving expensive cryptographic
        step redundant.}

        \resumeItem{Enabled rapid development iteration by developing bespoke
        simulation framework; published documentation and training resources.}

      \resumeItemListEnd

    \resumeSubheading
      {University of Maryland}{Aug. 2022 -- Present}
      {Teaching Assistant (Data Science / Intro to Computer Systems)}{College Park, MD}
      \resumeItemListStart

				\resumeItem{Led discussion sections with up to 40 students, fostering
        engaging learning environments.}

				\resumeItem{Mentored numerous students during office hours, clarifying
				intricate concepts related to \textbf{C}, \textbf{operating systems},
				and \textbf{data analysis}.}

      \resumeItemListEnd

    \resumeSubheading
      {The First-Year Innovation \& Research Experience @ University of Maryland}{Aug. 2020 -- Dec. 2021}
      {Undergraduate Research Assistant}{College Park, MD}
      \resumeItemListStart

				\resumeItem{Developed UNet-based \textbf{ML model} for LIDAR data \textbf{semantic
				segmentation}, achieving dense point classification within point clouds.}

				\resumeItem{Demonstrated project outcomes at an undergraduate research
				summit, showcasing successful contributions to LIDAR data analysis.}

      \resumeItemListEnd

% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects \& Awards}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{GeekOS} $|$ \emph{C}}{Aug. 2023 -- Present}
          \resumeItemListStart

            \resumeItem{Implemented crucial \textbf{OS} features in \textbf{C} as part of UMD's Operating Systems course.}
            \resumeItem{Added support for pipes, process control, signals, virtual memory (paging) and virtual filesystem.}

          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{OccupanSee} $|$ \underline{\href{https://devpost.com/software/occupan-see}{devpost:occupan-see}} $|$ \emph{Computer Vision, React, Python}}{Apr. 2023}
          \resumeItemListStart

            \resumeItem{Improved fire safety in large gatherings by automating
            overcrowding detection; received award from Bloomberg.}

            \resumeItem{Applied Facebook \textbf{Detectron2} model to
            quickly/accurately count people in webcam feed, then streamed
            real-time video to \textbf{React} app.}

          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Memaid} $|$ \underline{\href{https://devpost.com/software/memaid}{devpost:memaid}} $|$ \emph{Computer Vision, Speech To Text, NLP, Google Cloud, Python, Flutter}}{Apr. 2022}
          \resumeItemListStart

            \resumeItem{Furthered quality of life for dementia patients; received
            recognition by Google for innovative use of cloud technology.}

            \resumeItem{When someone introduces themselves to user,
            \textbf{Flutter} app applies \textbf{CV/NLP} to automatically
            memorize face/name and store conversation highlights. App relays
            name and conversation points during next interaction with individual
            through connected earbuds.}

          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Maskif.ai} $|$ \underline{\href{https://devpost.com/software/maskif-ai}{devpost:maskif-ai}} $|$ \emph{Computer Vision, IoT, TensorFlow, Python, Google Cloud}}{Nov. 2020}
          \resumeItemListStart

            \resumeItem{Developed accessible solution enforcing pandemic mask
            compliance; awarded grand prize at Yale's YHack 2020 hackathon.}

            \resumeItem{\textbf{Computer vision} intelligently triggers "smart" lock when
            unmasked individual approaches door; unlocks after individual's
            departure.}

            \resumeItem{Leverages \textbf{Google Assistant SDK} to support
            generic smart locks; fault-tolerant algorithm accurate with
            lower-quality cameras; efficient \textbf{neural network} performant
            on standard consumer hardware.}

          \resumeItemListEnd

    \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Rust, Python, Java, JavaScript, C/C++, Go, OCaml, Ruby, SQL, MATLAB, HTML, CSS} \\
     \textbf{Frameworks}{: Flask, React, React Native, Flutter, TensorFlow, PyTorch} \\
     \textbf{Tooling and Systems}{: Git, AWS, GCP, Docker, Linux} \\
     \textbf{Libraries}{: pandas, NumPy, Matplotlib} \\
     \textbf{General}{: Low-Level Systems}
    }}
 \end{itemize}
\end{document}